Estimating migrantation rates using kinship pairs \protect\thanks{Running head line: Estimating migrantation rates using kinship pairs}

### 2021-05-27 latex/ms.tex
add text in Theory

\title{Estimating migrant rates using kinship pairs \protect\thanks{Running head line: Estimating migrant rates using kinship pairs}}

@@

\subsection{Assumptions}

この章では，全てに共通するモデリングの仮定を述べた後，シンプルなモデルから徐々に複雑なモデルへと移行する。具体的には，最初にシンプルなモデルについて記述して，
\begin{itemize}
  \item 移動が双方向
  \item 性比1:1およびランダム交配を仮定して両性を考慮
  \item 繁殖ポテンシャルが一定でない
  \item 移動しやすさが繁殖ポテンシャルに依存
\end{itemize}
といった要素を追加していく。また，どのモデルでも共通して仮定しているのは以下の５点である。
\begin{enumerate}
  \item 年をまたぐ多回繁殖
  \item 親魚によるサブ集団間の移動は，繁殖シーズンの間に起きる
  \item サンプルされる当歳魚（０歳）は，必ずサンプルされたサブ集団で産まれる
  \item 当歳魚かどうかの判断は１００％可能
  \item サンプル間の近親判別では，１００％の成功率で半兄弟ペアか否かがなされる
\end{enumerate}
また，性成熟した個体を親と呼ぶことにする。

>>>>

\title{Estimating migrantation rates using kinship pairs \protect\thanks{Running head line: Estimating migrantation rates using kinship pairs}}

@@

\subsection{Hypothetical population and sampling scheme}

Suppose that we have a set of two populations labelled 1 and 2.

and there are migrant individuals between the two subpopulations. also no population subdivision or spatial struc- ture. In this study, a mature female is called a mother even if she does not produce offspring. For mathematical tractability, we assume that only one spawning ground exists in which the mothers remain for the entire spawning season. Following (Akita, 2020), our modeling frame- work employs two types of overdispersed reproduction: parental and nonparental variations. Thus, the former indicates a variation caused by the mother's covariates, such as age, weight, and residence time on the spawning ground, while the latter indicates a variation caused by nonrandom stochastic events during a series of reproductive episodes, which are independent of the mother's covariates, such as family-correlated survivorship or the mating behavior effects (e.g., competition for males/females and correlation between mating op- portunities of the mother and the number of her offspring). Figure 1 illustrates a schematic diagram of the effects of parental and non- parental variations exemplified by age-dependent reproduction and family-correlated survival on kinship relationships in a population. Detailed definitions of parental and nonparental variations are stated in (Akita, 2020). Appendix 1 provides the theoretical foundation of both parental and nonparental variations in reproduction.

\begin{itemize}
  \item 移動が双方向
  \item 性比1:1およびランダム交配を仮定して両性を考慮
  \item 繁殖ポテンシャルが一定でない
  \item 移動しやすさが繁殖ポテンシャルに依存
\end{itemize}
といった要素を追加していく。また，どのモデルでも共通して仮定しているのは以下の５点である。
\begin{enumerate}
  \item 年をまたぐ多回繁殖
  \item 親魚によるサブ集団間の移動は，繁殖シーズンの間に起きる
  \item サンプルされる当歳魚（０歳）は，必ずサンプルされたサブ集団で産まれる
  \item 当歳魚かどうかの判断は１００％可能
  \item サンプル間の近親判別では，１００％の成功率で半兄弟ペアか否かがなされる
\end{enumerate}
また，性成熟した個体を親と呼ぶことにする。
